\begin{frame}[allowframebreaks]\frametitle{References}
\tiny
\begin{thebibliography}{1}
   \bibitem{ref_fig_StandardModel} website: http://www.isgtw.org/spotlight/go-particle-quest-first-cern-hackfest
   \bibitem{ref_Griffiths} David Griffiths "Introduction to Elementary Particles", Wiley-VCH; 2nd edition (October 13, 2008)
   \bibitem{ref_fig_neutrinoScattering}http://www.quora.com/What-particles-would-result-from-electron-neutrino-scattering
   \bibitem{ref_fig_NeutronDecay2} http://www.astroblogs.nl/2013/07/15/nucleosynthese-en-de-oerknal/bb-nucleo-11-neutron-decay/
   \bibitem{ref_LBNFdoc_volume-physics} LBNF CDR draft, physics: https://lbne.bnl.gov/tmp/volume-physics.pdf
   \bibitem{ref_PDG} K.A. Olive et al. (Particle Data Group), Chin. Phys. C, 38, 090001 (2014) 
   \bibitem{ref_LBNFweb} LBNF website: http://lbnf.fnal.gov/
   \bibitem{ref_LisaWhitehead} personal e-mail by Prof. Lisa Whitehead
   \bibitem{ref_fig_pionandKaonDecays} website: http://cronodon.com/Atomic/EWT.html
   \bibitem{ref_LBN_OscExpReview} G. J. Feldman, J. Hartnell, T. Kobayashi, A Review of Long-baseline Neutrino Oscillation Experiments, Advances in High Energy Physics 2013 (2013), 475749
   \bibitem{ref_LBNF_CDR_volumeBeam} LBNF CDR draft, beam: http://lbne2-docdb.fnal.gov/cgi-bin/ RetrieveFile?docid=10686\&filename=Beamline\%20Annex\%20for\%20CDR\%20Vol3.pdf\&version=1
   \bibitem{ref_my_paper} paper for this exam: https://github.com/eavdeeva/Comprehensive\_LBNF/blob/master/Main.pdf
   \bibitem{ref_my_presentation} this presentation: https://github.com/eavdeeva/Comprehensive\_LBNF/blob/master/presentation\_Comprehensive\_LBNF.pdf
   \bibitem{ref_Homestake} Bruce T. Cleveland et. al., Measurement of the Solar Electron Neutrino Flux with the Homestake Chlorine Detector, 1998 Astrophysical Journal 496 505
   \bibitem{ref_SuperK} C.W.Walter, The Super-Kamiokande Experiment, Prepared for inclusion in "Neutrino Oscillations: Present Status and Future Plans", J. Thomas and P. Vahle editors, World Scientific Publishing Company, 2008. This version is 12 pages in REVTeX4 two-column format
   \bibitem{ref_SNO} John N. Bahcall, Global Analysis of Solar Neutrino Oscillations Including SNO CC Measurement, JHEP 0108:014,2001
   \bibitem{ref_fig_SNOscheme} website: http://ase.tufts.edu/cosmos/print\_images.asp?id=37
   \bibitem{ref_wiki_NeutrinoDetectors} website: http://en.wikipedia.org/wiki/Neutrino\_detector
   \bibitem{ref_fig_MuonDecay} website: http://www.hep.ucl.ac.uk/~jpc/all/ulthesis/node9.html
   \bibitem{ref_fig_NeutronDecay} website: http://en.wikipedia.org/wiki/Neutron
   \bibitem{ref_LBNFdoc_volume-detectors} LBNF CDR draft, detectors: https://lbne.bnl.gov/tmp/volume-detectors.pdf
   \bibitem{ref_LBNF_collaborationMeeting} Agenda of the first LBNF collaboration meeting: https://indico.fnal.gov/conferenceOtherViews.py? view=standard\&confId=9740
   \bibitem{ref_fig_cosmicMuons} website: http://hardhack.org.au/book/export/html/2
   \bibitem{ref_KEK} M. Ieiri et al. . Proceedings of the 11th Symposium on Accelerator Science and Technology, SPring-8, Harima Science Garden City, Hyogo, Japan pages 377–379 (1997)
   \bibitem{ref_NuMI} K. Anderson et al. The NuMI Facility Technical Design Report. FERMILAB-DESIGN-1998-01 (1998)
   \bibitem{ref_CNGS} G. Acquistapace et al. The CERN neutrino beam to Gran Sasso (NGS). CERN-98-02, INFN-AE-98-05, CERN-YELLOW-98-02 (1998)
   \bibitem{ref_JPARC} K. Abe et al. (T2K Collaboration). The T2K Experiment. Nucl.Instrum.Meth. A659, 106–135 (2011). [1106.1238.]
   \bibitem{ref_aboutLAr} website Fermilab today: http://www.fnal.gov/pub/today/archive/archive\_2014/today14-10-09.html
   \bibitem{ref_fig_oscProbability_with_LtoE} website: http://en.wikipedia.org/wiki/Neutrino\_oscillation
   \bibitem{ref_fig_solarNeutrinoSpectrum} Hans J. Haubold et. al. "Analysis of Solar Neutrino Data from Super-Kamiokande I and II" Entropy 2014, 16(3), 1414-1425; doi:10.3390/e16031414
   \bibitem{ref_fig_MendeleevTable} website: http://www.turnulsfatului.ro/11945/p-dou \%C3\%84\%C6\%92-elemente-noi-icirc-n-tabelul-lui-mendeleev-p-.html
   \bibitem{ref_U_parametrization} website: http://en.wikipedia.org/wiki/Pontecorvo\%E2\%80\%93Maki\%E2\%80\%93Nakagawa\%E2\%80\%93Sakata\_matrix
\end{thebibliography}
\end{frame}
