%\section{References}
\begin{thebibliography}{1}
   \bibitem{ref_PDG} K.A. Olive et al. (Particle Data Group), Chin. Phys. C, 38, 090001 (2014) 
   \bibitem{ref_Griffiths} David Griffiths "Introduction to Elementary Particles", Wiley-VCH; 2nd edition (October 13, 2008)
   \bibitem{ref_Homestake} Bruce T. Cleveland et. al., Measurement of the Solar Electron Neutrino Flux with the Homestake Chlorine Detector, 1998 Astrophysical Journal 496 505
   \bibitem{ref_SuperK} C.W.Walter, The Super-Kamiokande Experiment, Prepared for inclusion in "Neutrino Oscillations: Present Status and Future Plans", J. Thomas and P. Vahle editors, World Scientific Publishing Company, 2008. This version is 12 pages in REVTeX4 two-column format
   \bibitem{ref_SNO} John N. Bahcall, Global Analysis of Solar Neutrino Oscillations Including SNO CC Measurement, JHEP 0108:014,2001
   \bibitem{ref_LBN_OscExpReview} G. J. Feldman, J. Hartnell, T. Kobayashi, A Review of Long-baseline Neutrino Oscillation Experiments, Advances in High Energy Physics 2013 (2013), 475749
   \bibitem{ref_fig_StandardModel} website: http://www.isgtw.org/spotlight/go-particle-quest-first-cern-hackfest
   \bibitem{ref_LBNFdoc_volume-detectors} LBNF CDR draft, detectors: https://lbne.bnl.gov/tmp/volume-detectors.pdf
   \bibitem{ref_LBNFdoc_volume-physics} LBNF CDR draft, physics: https://lbne.bnl.gov/tmp/volume-physics.pdf
   \bibitem{ref_LBNFweb} LBNF website: http://lbnf.fnal.gov/
   \bibitem{ref_LBNF_collaborationMeeting} Agenda of the first LBNF collaboration meeting: https://indico.fnal.gov/conferenceOtherViews.py? view=standard\&confId=9740
   \bibitem{ref_KEK} M. Ieiri et al. . Proceedings of the 11th Symposium on Accelerator Science and Technology, SPring-8,
Harima Science Garden City, Hyogo, Japan pages 377–379 (1997)
   \bibitem{ref_NuMI} K. Anderson et al. The NuMI Facility Technical Design Report. FERMILAB-DESIGN-1998-01 (1998)
   \bibitem{ref_CNGS} G. Acquistapace et al. The CERN neutrino beam to Gran Sasso (NGS). CERN-98-02, INFN-AE-98-05,
CERN-YELLOW-98-02 (1998)
   \bibitem{ref_JPARC} K. Abe et al. (T2K Collaboration). The T2K Experiment. Nucl.Instrum.Meth. A659, 106–135 (2011).
[1106.1238.]
   \bibitem{ref_aboutLAr} website Fermilab today: http://www.fnal.gov/pub/today/archive/archive\_2014/today14-10-09.html
\end{thebibliography}
